Collapse Weddell and Check consistency

### 2023-08-25 WeddellSea_collapse.Rmd
Many changes

calc_topological_indices(gM)
write_csv(collapsed_w,"Data/Weddell_collapsed_links.csv")
```

>>>>

calc_topological_indices(gM)
write_csv(collapsed_w,"Data/Weddell_collapsed_links.csv")

collapsed_w <- read_csv("Data/Weddell_collapsed_links.csv")

# Weddell Sea get full classification

```{r, WeddellSeaFullClass, eval=F,echo=F,message=T,warning=T}
require(tidyverse)
require(igraph)
#
# Auxiliary functions
#
source("R/functions.R")

#
# Food-web data 
#
dtot <- read_csv("Data/WeddellSea_links_original.csv")

if( file.exists("Data/WeddellSea_clasification.rds")) {

  classall_df <- readRDS("Data/WeddellSea_clasification.rds")

} else {

  # Read complete clasification from Taxonomic databases
  #
  require(taxize)
  dfn <- unique(dtot$consumer)
  dfn <- c(dfn, unique(dtot$resource))
  dfn <- unique(dfn)

  # CLasificación completa

  clasall <- classification(dfn, db = 'gbif') #

  class_list <- class_to_df(clasall)

  classall_df <- class_list[[1]]

  #
  # Search in worms records Not found in gbif
  #

  dfn <- class_list[[2]]$Taxon

  clasall <- classification(dfn, db = 'worms') #

  class_list <- class_to_df(clasall)

  tmp_df <- class_list[[1]]
  names(tmp_df) <- tolower(names(tmp_df))
  names(tmp_df)[1] <- "Taxon"
  dfn <- class_list[[2]]$Taxon
  names(classall_df)
  classall_df <- bind_rows(classall_df,tmp_df)
  saveRDS(classall_df,file="Data/WeddellSea_clasification.rds")
}

# Search in any field of the df
#
search_value <- "foram"
result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))

# Replace the species nodes contained in `result` to the value of the field result$class 
# to obtain the degree of the collapsed node
#
search_value <- "Hexactinellida"
result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
dtot1 <- replace_nodes(dtot, result, "class")
collapsed_w <- dtot1 %>% distinct()
gM <- graph_from_edgelist(as.matrix(collapsed_w), directed  = T)

degree(gM)[search_value]

# Replace the species nodes contained in `result` to the value of the field result$class 
# to obtain the degree of the collapsed node
#
search_value <- "Bacillariophyceae"
result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))

dtot1 <- replace_nodes(dtot, result, "class")
collapsed_w <- dtot1 %>% distinct()
gM <- graph_from_edgelist(as.matrix(collapsed_w), directed  = T)

degree(gM)["Bacillariophyceae"]
degree(gM)["Pleuragramma antarcticum"]
require(NetIndices)
a <- get.adjacency(gM,sparse=F)
tl <- TrophInd(a)
tl[rownames(tl)=="Pleuragramma antarcticum",]
tl[rownames(tl)=="Pygoscelis adeliae",]
trophiclevels(gM)

search_value <- "Chromista"
result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))

search_value <- "Dictyocha"
result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
```
